\documentclass[12pt]{article}

\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{adjustbox}      
\usepackage{lscape}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{caption}
\usepackage{longtable}
\usepackage{multirow,rotating,array,booktabs,siunitx,blindtext}
\newcolumntype{C}{>{\centering\arraybackslash}p}
\usepackage{longtable,array,ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\arraybackslash\hspace{0pt}}p{#1}}
\usepackage[margin=0.02in]{geometry}

\begin{document}

\begin{landscape}
\begingroup
\setlength{\tabcolsep}{5pt} % Default value: 6pt

\renewcommand{\arraystretch}{1.5} % Default value: 1
\begin{longtable}{
@{}|
>{\raggedright}p{.5cm} |
>{\raggedright\arraybackslash}p{8.25cm}|
>{\raggedright\arraybackslash}p{8.5cm}@{}|
>{\raggedright\arraybackslash}p{8.25cm}|
p{6.5cm}|
@{}}
           \hline
\textbf{Sno} & \textbf{Variable} & \textbf{Actual Rscope}  & \textbf{Actual Wscope}\\
\hline
1 & Student. LoggedIn. SetRoom. room & [Student. LoggedIn. SetRoom] & [Student. LoggedIn. SetRoom] \\ 
\hline
2 & Student. LoggedOut. user & [tlogin] & [Student. LoggedOut] \\ 
\hline
3 & Student. LoggedIn. ViewDetails. room & [] & [Student. LoggedIn. ViewDetails] \\ 
\hline
4 & Student. LoggedIn. loggedinUser & [Student. LoggedIn. SetRoom, Student. LoggedIn. ViewDetails] & [tlogin] \\ 
\hline
5 & Student. LoggedIn. ViewDetails. student & [] & [Student. LoggedIn. ViewDetails] \\ 
\hline
6 & Student. rooms & [Student. LoggedIn. SetRoom, Student. LoggedIn. ViewDetails] & [Student. LoggedIn. SetRoom] \\ 
\hline
7 & Student. students & [tlogin] & [] \\ 
\hline
8 & Student. LoggedOut. password & [tlogin] & [Student. LoggedOut] \\ 
\hline

\caption{Actual R and W scope for Curfew1.txt}
\end{longtable}
\endgroup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begingroup
\setlength{\tabcolsep}{5pt} % Default value: 6pt

\renewcommand{\arraystretch}{1.5} % Default value: 1
        \begin{longtable}{
@{}|
>{\raggedright}p{.5cm} |
>{\raggedright\arraybackslash}p{8.25cm}|
>{\raggedright\arraybackslash}p{8.25cm}@{}|
>{\raggedright\arraybackslash}p{8.25cm}|
p{6.5cm}|
@{}}
\hline
\textbf{Sno} & \textbf{Variable} & \textbf{Actual Rscope}  & \textbf{Actual Wscope}\\
\hline
1 & Curfew. registration. userName & [Curfew. registration, register-success, register-failure] & [Curfew. registration] \\ 
\hline
2 & Curfew. LoggedIn. AdminDashboard. SetRoom. room & [Curfew. LoggedIn. AdminDashboard. SetRoom] & [Curfew. LoggedIn. AdminDashboard. SetRoom] \\ 
\hline
3 & Curfew. LoggedIn. student-dashboard. view-my-requests. myrequests & [] & [Curfew. LoggedIn. student-dashboard. view-my-requests] \\ 
\hline
4 & Curfew. LoggedIn. student-dashboard. request-curfew. request-LateOut. outTime & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-LateOut] \\ 
\hline
5 & Curfew. registration. usertype & [Curfew. registration] & [Curfew. registration] \\ 
\hline
6 & Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests. prsel & [pr-approve-pr, pr-proof-pr, pr-reject-pr] & [pr-select-pr] \\ 
\hline
7 & Curfew. LoggedIn. student-dashboard. request-curfew. request-LateOut. curfewLateOut-flag & [Curfew. LoggedIn. student-dashboard. request-curfew. request-LateOut] & [] \\ 
\hline
8 & Curfew. LoggedIn. AdminDashboard. view-requests. ticketid & [] & [] \\ 
\hline
9 & Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests. cr & [] & [Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests] \\ 
\hline
10 & Curfew. nulluser & [register-success, tlogout, register-failure] & [] \\ 
\hline
11 & Curfew. LoggedIn. student-dashboard. request-curfew. type-of-request & [Curfew. LoggedIn. student-dashboard. request-curfew] & [Curfew. LoggedIn. student-dashboard. request-curfew, Curfew. LoggedIn. student-dashboard. request-curfew. request-LateIn, Curfew. LoggedIn. student-dashboard. request-curfew. request-LateOut, Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] \\ 
\hline
12 & Curfew. LoggedOut. password & [tlogin-student, tlogin-admin] & [Curfew. LoggedOut, tlogout] \\ 
\hline
13 & Curfew. rooms & [Curfew. LoggedIn. AdminDashboard. ViewDetails, Curfew. LoggedIn. AdminDashboard. SetRoom] & [Curfew. LoggedIn. AdminDashboard. SetRoom] \\ 
\hline
14 & Curfew. nullRequest & [view-my-requests-upload-curfew-proof] & [] \\ 
\hline
15 & Curfew. LoggedIn. student-dashboard. request-curfew. student & [request-curfew-add-student] & [Curfew. LoggedIn. student-dashboard. request-curfew] \\ 
\hline
16 & Curfew. LoggedIn. loggedinUser & [Curfew. LoggedIn. AdminDashboard. ViewDetails, Curfew. LoggedIn. AdminDashboard. SetRoom, Curfew. LoggedIn. student-dashboard. view-my-requests, Curfew. LoggedIn. student-dashboard. request-curfew, tlogin-student, tlogin-admin] & [tlogin-student, tlogin-admin] \\ 
\hline
17 & Curfew. LoggedIn. loggedinUsertype & [tsetroom, tviewdetails] & [tlogin-student, tlogin-admin] \\ 
\hline
18 & Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests. rr & [] & [Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests] \\ 
\hline
19 & Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests. pending-flag & [Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests, pr-approve-pr, pr-reject-pr] & [Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests] \\ 
\hline
20 & Curfew. registration. user & [register-success] & [Curfew. registration] \\ 
\hline
21 & Curfew. LoggedIn. AdminDashboard. ViewDetails. room & [] & [Curfew. LoggedIn. AdminDashboard. ViewDetails] \\ 
\hline
22 & Curfew. LoggedIn. student-dashboard. request-curfew. reason & [Curfew. LoggedIn. student-dashboard. request-curfew] & [Curfew. LoggedIn. student-dashboard. request-curfew] \\ 
\hline
23 & Curfew. requests & [Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests, Curfew. LoggedIn. student-dashboard. view-my-requests, Curfew. LoggedIn. student-dashboard. request-curfew, Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests, Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests, Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests, pr-approve-pr, vacation-init-success, pr-reject-pr, LateIn-init-success, curfew-init-success] & [Curfew. LoggedIn. student-dashboard. request-curfew, vacation-init-success, LateIn-init-success, curfew-init-success] \\ 
\hline
24 & Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests. closed-flag & [Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests] & [Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests] \\ 
\hline
25 & Curfew. LoggedIn. student-dashboard. request-curfew. teamlist & [request-curfew-add-student] & [Curfew. LoggedIn. student-dashboard. request-curfew, request-curfew-add-student] \\ 
\hline
26 & Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests. pr & [pr-select-pr] & [Curfew. LoggedIn. AdminDashboard. view-requests. pending-requests, pr-approve-pr, pr-reject-pr] \\ 
\hline
27 & Curfew. LoggedOut. user & [tlogin-student, tlogin-admin] & [Curfew. LoggedOut, tlogout] \\ 
\hline
28 & Curfew. nulllist & [pr-approve-pr, pr-proof-pr, pr-reject-pr] & [] \\ 
\hline
29 & Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation. inDate & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] \\ 
\hline
30 & Curfew. students & [Curfew. LoggedIn. AdminDashboard. ViewDetails, Curfew. LoggedIn. AdminDashboard. SetRoom, Curfew. LoggedIn. student-dashboard. view-my-requests, Curfew. LoggedOut] & [] \\ 
\hline
31 & Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation. vacation-flag & [Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] & [] \\ 
\hline
32 & Curfew. userType & [] & [] \\ 
\hline
33 & Curfew. LoggedIn. AdminDashboard. ViewDetails. student & [] & [Curfew. LoggedIn. AdminDashboard. ViewDetails] \\ 
\hline
34 & Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation. outDate & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] \\ 
\hline
35 & Curfew. LoggedOut. username & [Curfew. LoggedOut] & [Curfew. LoggedOut] \\ 
\hline
36 & Curfew. LoggedIn. student-dashboard. upload-curfew-proof. sReq & [] & [view-my-requests-upload-curfew-proof] \\ 
\hline
37 & Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation. outTime & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] \\ 
\hline
38 & Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests. rejected-flag & [Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests] & [Curfew. LoggedIn. AdminDashboard. view-requests. rejected-requests] \\ 
\hline
39 & Curfew. LoggedIn. student-dashboard. view-my-requests. selectedRequest & [view-my-requests-upload-curfew-proof] & [Curfew. LoggedIn. student-dashboard. view-my-requests] \\ 
\hline
40 & Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests. cr & [] & [Curfew. LoggedIn. AdminDashboard. view-requests. closed-requests] \\ 
\hline
41 & Curfew. registeredUsers & [register-success, tlogin-student, tlogin-admin, register-failure] & [register-success] \\ 
\hline
42 & Curfew. registration. password & [Curfew. registration] & [Curfew. registration] \\ 
\hline
43 & Curfew. LoggedIn. student-dashboard. request-curfew. request-LateIn. inTime & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-LateIn] \\ 
\hline
44 & Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests. approved-flag & [Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests] & [Curfew. LoggedIn. AdminDashboard. view-requests. approved-requests] \\ 
\hline
45 & Curfew. LoggedIn. student-dashboard. upload-curfew-proof. document & [] & [Curfew. LoggedIn. student-dashboard. upload-curfew-proof] \\ 
\hline
46 & Curfew. LoggedIn. student-dashboard. request-curfew. request & [Curfew. LoggedIn. student-dashboard. request-curfew, vacation-init-success, LateIn-init-success, curfew-init-success] & [Curfew. LoggedIn. student-dashboard. request-curfew] \\ 
\hline
47 & Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation. inTime & [] & [Curfew. LoggedIn. student-dashboard. request-curfew. request-vacation] \\ 
\hline
48 & Curfew. LoggedIn. student-dashboard. request-curfew. request-LateIn. curfewLateIn-flag & [Curfew. LoggedIn. student-dashboard. request-curfew. request-LateIn] & [] \\ 
\hline


\caption{Actual R and W scope for Curfewfull.txt}

\end{longtable}

\endgroup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\begin{adjustbox}{width={1.5\textwidth},totalheight={\textheight},keepaspectratio}
\begingroup
\setlength{\tabcolsep}{5pt} % Default value: 6pt

\renewcommand{\arraystretch}{1.5} % Default value: 1
        \begin{longtable}{
@{}|
>{\raggedright}p{.5cm} |
>{\raggedright\arraybackslash}p{8.25cm}|
>{\raggedright\arraybackslash}p{8.25cm}@{}|
>{\raggedright\arraybackslash}p{8.25cm}|
p{6.5cm}|
@{}}
        
\textbf{Sno} & \textbf{Variable} & \textbf{Actual Rscope}  & \textbf{Actual Wscope}\\
\hline
1 & hms. admintype & [LoggedOut-LoggedIn-AdminModule] & [hms] \\ 
\hline
2 & hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints. compliantPriority & [] & [hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints] \\ 
\hline
3 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. deadline1 & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
4 & hms. LoggedIn. StudentModule. ScheduleHouseKeeping. EnterVacation. inTime & [] & [] \\ 
\hline
5 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. roomno & [] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment] \\ 
\hline
6 & hms. LoggedIn. AdminModule. HostelManagement. RoomAddition. no & [RoomAddition-RoomAddition] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAddition] \\ 
\hline
7 & hms. centraladmintype & [LoggedOut-LoggedIn-CentralAdminModule] & [hms] \\ 
\hline
8 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. student & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment, RoomAllotment-RoomAllotment] & [StudentSelection-RoomSelection] \\ 
\hline
9 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. StudentSelection. selectedStudent & [StudentSelection-RoomSelection] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. StudentSelection] \\ 
\hline
10 & hms. departments & [DepartmentAddition-Done] & [DepartmentAddition-Done] \\ 
\hline
11 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition. rno & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] \\ 
\hline
12 & hms. LoggedIn. AdminModule. StudentManagement. SendGroupMessages. message & [SendGroupMessagesDone] & [hms. LoggedIn. AdminModule. StudentManagement. SendGroupMessages] \\ 
\hline
13 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. deadline3 & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
14 & hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByName. name & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByName] & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByName] \\ 
\hline
15 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. wing & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment, RoomAllotment-RoomAllotment] & [RoomSelection-StudentSelection] \\ 
\hline
16 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. deadline2 & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
17 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. emailID & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
18 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. usertype & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
19 & hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints. key & [hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints] & [hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints] \\ 
\hline
20 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. room & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment, RoomAllotment-RoomAllotment] & [RoomSelection-StudentSelection] \\ 
\hline
21 & hms. LoggedIn. AdminModule. StudentManagement. SendGroupMessages. studList & [SendGroupMessagesDone] & [StudentSearch-SendGroupMessages] \\ 
\hline
22 & hms. LoggedIn. AdminModule. UserManagement. ViewUsers. selectedUser & [] & [hms. LoggedIn. AdminModule. UserManagement. ViewUsers, EnableUserDone, DisableUserDone] \\ 
\hline
23 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. rollno & [] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment] \\ 
\hline
24 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. newpolicy & [CreateEscalationPolicy-Done] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
25 & hms. LoggedIn. AdminModule. StudentManagement. FineStudents. reason & [FineStudentsDone] & [hms. LoggedIn. AdminModule. StudentManagement. FineStudents] \\ 
\hline
26 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. firstOfficer & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
27 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. WardenAddition. buildingIncharge & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. WardenAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. WardenAddition] \\ 
\hline
28 & hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints. problemStartDate & [] & [hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints] \\ 
\hline
29 & hms. complaints & [hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints, ForwardComplaints-ComplaintView, ResolveComplaints-ComplaintView] & [ForwardComplaints-ComplaintView, ResolveComplaints-ComplaintView] \\ 
\hline
30 & hms. complaintResolved & [hms. LoggedIn. AdminModule. ComplaintManagement. ResolveComplaints] & [hms] \\ 
\hline
31 & hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. ComplaintDetail. sComplaint & [] & [SearchComplaints-ComplaintsDetail] \\ 
\hline
32 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition. stud & [StudentAdditionDone] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition, StudentAdditionDone] \\ 
\hline
33 & hms. complaintAssigned & [] & [hms] \\ 
\hline
34 & hms. LoggedIn. AdminModule. StudentManagement. FineStudents. fineID & [FineStudentsDone] & [] \\ 
\hline
35 & hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints. complaintDescription & [] & [hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints] \\ 
\hline
36 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. RoomSelection. selectedRoom & [RoomSelection-StudentSelection] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. RoomSelection] \\ 
\hline
37 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. contactno & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
38 & hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. selectedStudent & [StudentSearch-FineStudents, StudentSearch-SendGroupMessages] & [Search-SearchByName, Search-SearchByRollNo] \\ 
\hline
39 & hms. LoggedIn. WorkerModule. MarkAttendance. punchTime & [MarkAttendance-Done] & [] \\ 
\hline
40 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition. department & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] \\ 
\hline
41 & hms. LoggedIn. AdminModule. HostelManagement. WingAddition. newwing & [WingAddition-WingAddition] & [hms. LoggedIn. AdminModule. HostelManagement. WingAddition] \\ 
\hline
42 & hms. complaintLaunched & [] & [hms] \\ 
\hline
43 & hms. workertype & [LoggedOut-LoggedIn-WorkerModule] & [] \\ 
\hline
44 & hms. LoggedIn. loggedInUser & [MarkAttendance-Done] & [LoggedOut-LoggedIn-StudentModule, LoggedOut-LoggedIn-AdminModule, MarkAttendance-Done, LoggedOut-LoggedIn-EscalationModule, LoggedOut-LoggedIn-CentralAdminModule, LoggedOut-LoggedIn-WorkerModule] \\ 
\hline
45 & hms. wardens & [WardenAdditionDone] & [WardenAdditionDone] \\ 
\hline
46 & hms. LoggedIn. AdminModule. HostelManagement. RoomAddition. newRoom & [RoomAddition-RoomAddition] & [RoomAddition-RoomAddition] \\ 
\hline
47 & hms. LoggedIn. AdminModule. HostelManagement. RoomAddition. occupancy & [RoomAddition-RoomAddition] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAddition] \\ 
\hline
48 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. newuser & [WardenAdditionDone, StudentAdditionDone] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
49 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. username & [hms. LoggedIn. AdminModule. UserManagement. UserAddition, WardenAdditionDone, StudentAdditionDone] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
50 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. thirdOfficer & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
51 & hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. RoomSelection. selectedWing & [RoomSelection-StudentSelection] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAllotment. RoomSelection] \\ 
\hline
52 & hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints. selectedComplaint & [SearchComplaints-ComplaintsDetail] & [hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints] \\ 
\hline
53 & hms. complaintAcknowledged & [] & [hms] \\ 
\hline
54 & hms. registeredUsers & [hms. LoggedOut, hms. LoggedIn. AdminModule. UserManagement. ViewUsers, WardenAdditionDone, EnableUserDone, DisableUserDone, UserDeletionDone, StudentAdditionDone] & [WardenAdditionDone, StudentAdditionDone] \\ 
\hline
55 & hms. LoggedIn. StudentModule. ScheduleHouseKeeping. EnterVacation. outTime & [] & [] \\ 
\hline
56 & hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints. c & [ForwardComplaints-ComplaintView] & [hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints, ComplaintsView-ForwardComplaints] \\ 
\hline
57 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. secondOfficer & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
58 & hms. LoggedIn. AdminModule. ComplaintManagement. ComplaintsView. selectedComplaint & [ComplaintsView-ResolveComplaints, ComplaintsView-ForwardComplaints] & [hms. LoggedIn. AdminModule. ComplaintManagement. ComplaintsView] \\ 
\hline
59 & hms. complaintForwarded & [hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints] & [hms] \\ 
\hline
60 & hms. LoggedOut. enteredUser & [LoggedOut-LoggedIn-StudentModule, LoggedOut-LoggedIn-AdminModule, LoggedOut-LoggedIn-EscalationModule, LoggedOut-LoggedIn-CentralAdminModule, LoggedOut-LoggedIn-WorkerModule] & [hms. LoggedOut, LoggedIn-LoggedOut] \\ 
\hline
61 & hms. LoggedIn. AdminModule. HostelManagement. CloseRoom. selectedWing & [CloseRoom-CloseRoom] & [CloseRoom-CloseRoom] \\ 
\hline
62 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. thirdOfficer & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
63 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. password & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
64 & hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition. newDepartment & [DepartmentAddition-Done] & [DepartmentAddition-Done] \\ 
\hline
65 & hms. LoggedOut. pass & [LoggedOut-LoggedIn-StudentModule, LoggedOut-LoggedIn-AdminModule, LoggedOut-LoggedIn-EscalationModule, LoggedOut-LoggedIn-CentralAdminModule, LoggedOut-LoggedIn-WorkerModule] & [hms. LoggedOut, LoggedIn-LoggedOut] \\ 
\hline
66 & hms. LoggedIn. AdminModule. HostelManagement. WingAddition. name & [hms. LoggedIn. AdminModule. HostelManagement. WingAddition, WingAddition-WingAddition] & [hms. LoggedIn. AdminModule. HostelManagement. WingAddition] \\ 
\hline
67 & hms. LoggedIn. AdminModule. HostelManagement. CloseRoom. wing-name & [CloseRoom-CloseRoom] & [hms. LoggedIn. AdminModule. HostelManagement. CloseRoom] \\ 
\hline
68 & hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition. departmentName & [DepartmentAddition-Done] & [hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition] \\ 
\hline
69 & hms. studenttype & [LoggedOut-LoggedIn-StudentModule] & [hms] \\ 
\hline
70 & hms. LoggedIn. AdminModule. StudentManagement. FineStudents. newFine & [FineStudentsDone] & [FineStudentsDone] \\ 
\hline
71 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. WardenAddition. w & [WardenAdditionDone] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. WardenAddition, WardenAdditionDone] \\ 
\hline
72 & hms. LoggedIn. AdminModule. StudentManagement. FineStudents. amount & [FineStudentsDone] & [hms. LoggedIn. AdminModule. StudentManagement. FineStudents] \\ 
\hline
73 & hms. LoggedIn. AdminModule. UserManagement. ViewUsers. username & [hms. LoggedIn. AdminModule. UserManagement. ViewUsers, EnableUserDone, DisableUserDone, UserDeletionDone] & [hms. LoggedIn. AdminModule. UserManagement. ViewUsers] \\ 
\hline
74 & hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition. contactno & [DepartmentAddition-Done] & [hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition] \\ 
\hline
75 & hms. wings & [CloseRoom-CloseRoom, WingAddition-WingAddition] & [WingAddition-WingAddition] \\ 
\hline
76 & hms. LoggedOut. uname & [hms. LoggedOut] & [hms. LoggedOut, LoggedIn-LoggedOut] \\ 
\hline
77 & hms. LoggedIn. AdminModule. HostelManagement. CloseRoom. roomno & [CloseRoom-CloseRoom] & [hms. LoggedIn. AdminModule. HostelManagement. CloseRoom] \\ 
\hline
78 & hms. LoggedIn. AdminModule. HostelManagement. CloseRoom. selectedRoom & [CloseRoom-CloseRoom] & [CloseRoom-CloseRoom] \\ 
\hline
79 & hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. key & [Search-SearchByName, Search-SearchByRollNo] & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByName, hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByRollNo] \\ 
\hline
80 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition. batchOfJoining & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition. StudentAddition] \\ 
\hline
81 & hms. LoggedIn. AdminModule. UserManagement. UserAddition. confirmpassword & [] & [hms. LoggedIn. AdminModule. UserManagement. UserAddition] \\ 
\hline
82 & hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints. complaintArea & [] & [hms. LoggedIn. StudentModule. ComplaintModule. MakeComplaints] \\ 
\hline
83 & hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy. secondOfficer & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. CreateEscalationPolicy] \\ 
\hline
84 & hms. complaintRejected & [] & [hms] \\ 
\hline
85 & hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints. toDepartment & [hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints, ForwardComplaints-ComplaintView] & [hms. LoggedIn. AdminModule. ComplaintManagement. ForwardComplaints] \\ 
\hline
86 & hms. students & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByName, hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByRollNo, Search-SearchByName, StudentAdditionDone, Search-SearchByRollNo] & [StudentAdditionDone] \\ 
\hline
87 & hms. LoggedIn. AdminModule. WorkerManagement. WorkersView. departmentid & [] & [hms. LoggedIn. AdminModule. WorkerManagement. WorkersView] \\ 
\hline
88 & hms. complaintReviewedandPropogated & [] & [hms] \\ 
\hline
89 & hms. LoggedIn. AdminModule. WorkerManagement. WorkersView. workerList & [] & [] \\ 
\hline
90 & hms. centreheadtype & [LoggedOut-LoggedIn-EscalationModule] & [hms] \\ 
\hline
91 & hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByRollNo. no & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByRollNo] & [hms. LoggedIn. AdminModule. StudentManagement. StudentSearch. SearchByRollNo] \\ 
\hline
92 & hms. LoggedIn. AdminModule. StudentManagement. FineStudents. stud & [FineStudentsDone] & [StudentSearch-FineStudents, FineStudentsDone] \\ 
\hline
93 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. firstOfficer & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
94 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. deadline1 & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
95 & hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition. departmentHead & [DepartmentAddition-Done] & [hms. LoggedIn. AdminModule. WorkerManagement. DepartmentAddition] \\ 
\hline
96 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. deadline2 & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
97 & hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy. deadline3 & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy] \\ 
\hline
98 & hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints. complaintList & [] & [hms. LoggedIn. CentralAdminModule. ViewEscalatedComplaints. SearchComplaints] \\ 
\hline
99 & hms. LoggedIn. AdminModule. ComplaintManagement. ResolveComplaints. c & [ResolveComplaints-ComplaintView] & [hms. LoggedIn. AdminModule. ComplaintManagement. ResolveComplaints, ComplaintsView-ResolveComplaints] \\ 
\hline
100 & hms. LoggedIn. AdminModule. HostelManagement. RoomAddition. selectedWing & [RoomAddition-RoomAddition] & [hms. LoggedIn. AdminModule. HostelManagement. RoomAddition, RoomAddition-RoomAddition] \\ 
\hline
101 & hms. policy & [Dashboard-EnableEscalationPolicy, Dashboard-CreateEscalationPolicy, Dashboard-DisableEscalationPolicy, Dashboard-ChangeEscalationPolicy, CreateEscalationPolicy-Done] & [hms. LoggedIn. CentralAdminModule. ChangeEscalationPolicy, Dashboard-EnableEscalationPolicy, Dashboard-DisableEscalationPolicy, CreateEscalationPolicy-Done] \\ 
\hline
 
\caption{Actual R and W scope for hmsnew.txt}

\end{longtable}
\endgroup


%\end{adjustbox}
%\caption{Actual R and W scope for Curfew1.txt}
%\end{table}
\end{landscape}
\end{document}
